---
title: "Hooper_Lab_7_206"
author: "Tess Hooper"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey it's Tess!


Hey, it's Tess again --- why did the dinosaur cross the road? 

To escape death ? 
<<<<<<< HEAD
Because the light was green 

Nope... chickens didn't exist yet

Blue 



Creator (Tess)

Getting gc_df.csv data, loading the tidyverse, and getting some summary counts 

```{r}

library(tidyverse)
gc_df <- read_csv("gc_df.csv")


get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>%  #Makes a table that groups gender and gun control preference -- as is here, this is not in contingency format (we want one row for male and one row for female)
  spread(make_get_guns, n) %>% #Spreads out data so variables (male and female) exist in their own columns (rather than separate columns based on gun preference) 
  select(-gender) #Removes gender column and makes it labeled just "1" and "2"

rownames(get_guns) <- c("Female", "Male") #Renames row names "1" and "2" as Female and Male

```
I am the Collaborator ( VGuenther2) and I am going to chi_square 
Is there a significant difference in gun control perspectives ( as related to access to guns)for males and females ?

Is there a significant association between sex and gun control recommendations ?

Chi-Square
```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1) # only calculate accross rows 
guns_prop

#Performing chi-square
guns_x2 <- chisq.test(get_guns)
guns_x2
```
Recommended gvmt action on gun access differs significantly for males and females($\chi^2$(`r guns_x2$parameter`)=......, p <0.001)


xxxxxx





I am the other Collaborator (Karan) and I am also going to do chi-square.

Is the perception of gun control access independent of sex?

```{r}

guns_prop = prop.table(as.matrix(get_guns), 1)

guns_prop

# Perform chi-square

guns_x2 = chisq.test(get_guns)
guns_x2

```

